### 2016-01-07 pdocs/thesis/introduction.tex
pdocs

Physics engines is active research area on many research and industry areas.
Especially gaming and movie industry are powerful drivers.
Robotics is typical research areas that uses physics engines.

@@

\cite{cornell.cs3152}

@@

Target of this work is to find out suitable methods for handling of plasticity in bulletphysics, \cite{bulletphysics}. 
Handling of plasticity basically means that objects involved may absorb kinetic energy and break.

>>>>

Physics engines is active research area on many research and industry areas.
Especially gaming and movie industry are powerful drivers.
Robotics is typical research areas that uses physics engines.
In \lut simulation of working machines has been active research area, e.g. \cite{moisio.thesis}.

@@

E.g. \cite{cornell.cs3152} and \cite{cornell.cs5643} are good examples of modern university cources
about physics engines. They also provide additional resources on used technologies.

@@

Target of this work is to find out suitable methods for handling of plasticity and verify them 
in commonly used physics engine bulletphysics, \cite{bulletphysics}. 
Handling of plasticity basically means that objects involved may absorb kinetic energy and break.

### 2016-01-07 pdocs/thesis/nimio.tex
pdocs

%\vspace{4mm}
{\sffamily\footnotesize Thesis for the degree of Doctor of Science (Technology) to be presented with\\
due permission for public examination and criticism in the Auditorium ...\\
at Lappeenranta University of Technology, Lappeenranta, Finland on the\\
..th of \mymonth, \myyear, at noon.}\\

>>>>

%\vspace{4mm}
{\sffamily\footnotesize Thesis for the degree of Doctor of Science (Technology) to be presented with\\
due permission for public examination and criticism in the Auditorium ...\\
at \lut, Lappeenranta, Finland on the\\
..th of \mymonth, \myyear, at noon.}\\
